Kalman tracking and estimation of continuous gravitational waves with a pulsar timing array

### 2023-08-07 docs/manuscript/paper.tex
create PP plots, N=200

\subsubsection{Detection}
We frame the detection problem in terms of a Bayesian model selection procedure as described in Section \ref{sec:model_selection}.

The Bayes factor $\beta$ as defined in Eq. \ref{eq:bayes} is presented in Fig \ref{fig:bayes} for our representative example system, where we now vary the magnitude of the GW strain, $h_0$.

The noise is an identical realisation for each value of $h_0$

We take $\beta = 10$ as a tolerance cutoff above which we can accept $\mathcal{M}_1$ and claim a detection of the GW.

For this system, given this realisation of the noise, the minimal detectable strain is $\sim 3 \times 10^{-15}$

The small perturbations in the general log-linear $\beta - h_0$ trend arise due to noise in the nested sampling method. For these points the sampler did not converge as well for $\mathcal{M}_1$ and so the evidence is lower than would be expected. This is purely a noise artefact: running the nested sampler again and recreating the $\beta - h_0$ leads to either no perturbations, or perturbations at different points in the curve.

Below $\beta = 10$ this noise in the sampler starts to dominate and the hierarchical structure of the models $\mathcal{M}_0 , \mathcal{M}_1$ fails. That is, the requirement that $\mathcal{Z}(\boldsymbol{Y} | \mathcal{M}_1) > \mathcal{Z}(\boldsymbol{Y} | \mathcal{M}_0)$ no longer holds

and the $\beta - h_0$ curve becomes much less smooth

This is simply stating that at these small strains the system is completely noise dominated and the two models $\mathcal{M}_1, \mathcal{M}_0$ cannot be separated.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/PaperBayesRatioPlotn1000_stacked}
	\caption{}
	\label{fig:bayes}
\end{figure}

@@

\subsection{Bias by dropping pulsar terms}

>>>>

\subsubsection{Detection}
We frame the problem of claiming a detection of a GW in the noisy data in terms of a Bayesian model selection procedure as described in Section \ref{sec:model_selection}. The Bayes factor, $\beta$, as defined in Eq. \ref{eq:bayes} is presented in Fig \ref{fig:bayes} for our representative system, where we now vary the magnitude of the GW strain, $h_0$. The noise processes in the synthetic data are identical realisations for each value of $h_0$; the only change in the data is the change in $h_0$. We can see that there is a general log-linear relationship between $\beta$ and $h_0$ where the GW source is easily detectable with decisive evidence ($\beta \sim 100$) for $h_0 \gtrapprox 10^{-14}$. We take $\beta = 10$ as a tolerance cut-off above which we can accept $\mathcal{M}_1$ and claim a detection of the GW. For this system, given this realisation of the noise, the minimal detectable strain is $\sim 3 \times 10^{-15}$. The small perturbations in the general log-linear $\beta - h_0$ trend arise due to noise in the nested sampling method. For these points the sampler converged sub-optimally for $\mathcal{M}_1$ and so the evidence $\mathcal{Z}(\boldsymbol{Y} | \mathcal{M}_1)$ is lower than would be expected. This is purely a noise artefact; if one recreates the $\beta - h_0$ curve by rerunning the nested sampler these perturbations appear at different values of $h_0$, or else are not present at all. Increasing the number of live points $n_{\rm live}$ used by the nested sampler also dampens these perturbations and smooths the $\beta - h_0$ curve, since as discussed in Section \ref{sec:nested_sampling} the uncertainties in $\mathcal{Z}$ scale as $\mathcal{O}(1/ \sqrt{n_{\rm live}})$. Below $\beta = 10$ this noise in the sampler starts to dominate and the hierarchical relationship between $\mathcal{M}_0$ and  $\mathcal{M}_1$ fails. That is, the requirement that $\mathcal{Z}(\boldsymbol{Y} | \mathcal{M}_1) > \mathcal{Z}(\boldsymbol{Y} | \mathcal{M}_0)$ no longer holds. This is simply due to the fact that at these small strains the system is completely noise dominated and the two models $\mathcal{M}_1, \mathcal{M}_0$ cannot be separated.  
\begin{figure}
	\includegraphics[width=\columnwidth]{images/PaperBayesRatioPlotn1000_stacked}
	\caption{Bayes ratio $\beta$ between the competing models $\mathcal{M_1}$ (GW present in data) and $M_0$ (GW not present in data) at different GW strain magnitudes $,h_0$, for the representative example summarised in Table \ref{tab:parameters_and_priors}. The horizontal grey dashed line labels the detection tolerance cut-off of $\beta = 10$. The minimal detectable strain, below which $\beta < 10$, is $\sim 3 \times 10^{-15}$.}
	\label{fig:bayes}
\end{figure}

@@

can we also get a sky map using the KF? 
\subsection{Bias by dropping pulsar terms}
